### 2012-05-23 inst/examples/policycosts/free_decrease.Rmd
updated examples with corrected policy adjustment costs in the simulation

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="fixed/" or`

@@

# Policy Costs fixed fee 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 9.103
penalty <- fixed(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

>>>>

`ro message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="free_decrease/" or`

@@

# Asymmetric Policy Costs, decreases to quota are free 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- free_decrease(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

### 2012-05-23 inst/examples/policycosts/free_increase.Rmd
updated examples with corrected policy adjustment costs in the simulation

`ro message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="free_decrease/" or`

@@

# Asymmetric Policy Costs, decreases to quota are free 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- free_decrease(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

>>>>

`ro message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="free_increase/" or`

@@

# Asymmetric Policy Costs, increases to quota are free 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- free_increase(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````
